---
title: "Programming Background"
author: "Shaniqua A. Walker"
date: "9/14/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "../images/")
```

```{r, eval=FALSE}
library(usethis)
use_git_config(user.name = "ShaniquaWalker", user.email = "sawalke4@ncsu.edu")
rmarkdown::render("2021-9-14-Second-Blog-Post.Rmd", 
                  output_format = "github_document", 
                  output_dir = "../_posts/",
                  output_options = list(html_preview = FALSE, keep_html = FALSE))
```

## My Experience With Programming

### R vs. SAS
When it comes to R, I enjoy the language way more than SAS. I'm not sure how I can explain it better but I believe that the R language is more straightforward and easier to understand, unlike SAS. 

The functionality I like about R is the way it is a glorified calculator while also being a service that allows the user to create various types of documents that show many different ways of showing data. 

I honestly do not miss much about SAS.

I would say R language is medium as far as difficulty to learn. My first experience with R was in 563 and, although there was a book that helped me understand some basic functions and setups that R can pull off, this course has increased the little things that I did not catch on to quickly.

```{r}
plot(airquality)
```